TacticToe: Learning the Game of Tactics

### 2018-01-24 tactictoe_jv.tex
scaling distribution

All experiments in this table are using orthogonalization.
\begin{table}[t]
\centering\ra{1.3}
\small
\begin{tabular}{ll}
\toprule
  & Solved \\
\midrule
% holyhammer & 79 \\
 none & 122\\
 ortho & 129\\
 ortho + term & 126\\    
 ortho + theorem list & 160\\
 ortho + metis & 162\\
 %ortho + metis + thmortho & 155\\
 %ortho + metis + stacortho & 160\\
 ortho + metis + theorem list & 175\\ 
\bottomrule
\end{tabular}
\caption{\label{tab:cfot_param}
Sucess rates of tactictoe with synthesis for different arguments.}
\end{table}
We want to know what the optimal number of predictions for tactics different 
from \metis since \metis has a special status in our algorithm is handled 
independently.

@@

\begin{figure}[h]
\centering           
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=2000,
  xmin=0, xmax=10,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\end{axis}
\end{tikzpicture}     
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=120,
  xmin=10, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\legend{\tactictoe,original}
\end{axis}
\end{tikzpicture}
\caption{Distribution of the proof length in tactic unit of evaluated theorems.}
\end{figure}

Analysing failed proof attempt can give us an idea of the behaviour of the 
algorithm. In a proof search of 10 seconds, in average 500 (todo: real 
estimation) tactics are applied.
The productive tactics create an average of 100 (todo: real estimation) nodes. 
This means that in this settings 1 out of 5 tactics are productive.

>>>>

All experiments in this table are using orthogonalization.
\begin{table}[t]
\centering\ra{1.3}
\small
\begin{tabular}{ll}
\toprule
  & Solved \\
\midrule
% holyhammer & 79 \\
 none & 122\\
 ortho & 129\\
 ortho + term & 126\\    
 ortho + theorem list & 160\\
 ortho + \metis & 162\\
 %ortho + metis + thmortho & 155\\
 %ortho + metis + stacortho & 160\\
 ortho + \metis + theorem list & 175\\ 
\bottomrule
\end{tabular}
\caption{\label{tab:cfot_param}
Sucess rates of tactictoe with synthesis for different arguments.}
\end{table}
We want to know what the optimal number of predictions for tactics different 
from \metis since \metis has a special status in our algorithm is handled 
independently.

@@

\begin{figure}[h]
\centering           
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=3000,
  xmin=0, xmax=10,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\end{axis}
\end{tikzpicture}     
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=120,
  xmin=10, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\legend{scaled \tactictoe,original}
\end{axis}
\end{tikzpicture}
\caption{Number of original proofs with a number $x$ of tactic units. 
         Since there is about two-third of the original proofs that have a 
         respective \tactictoe proofs, we scale the number of 
         \tactictoe proofs by a factor of $\frac{1}{0.662}$.. 
\tactictoe 
 proofs.}
\end{figure}
